Backward Population Synthesis: Mapping the Evolutionary History of Gravitational-Wave Progenitors

### 2023-03-20 src/tex/ms.tex
Add changes about table 1

We apply the method described in section \ref{subsec:stats} to the
first GW event GW150914 \citep{GW150914}. We use the \texttt{Overall\_posterior}
posterior samples for GW150914, publicly available from the Gravitational wave
Open Science Center \citep{LIGOScientific:2019lzm}. The parameters involved in
the analysis and the range we allow for the inference are tabulated in table
\ref{tab:parameters}. The spin of BHs formed in isolated binaries depends
strongly on the angular momentum transport in massive stars which is still
highly uncertain (see however \citet{Fuller2019, Bavera2020}), therefore we only
consider the two component masses in the observable space $\bm{\theta}$ in both
the root-finding stage and the MCMC stage. Instead of the sampling the posterior
in the two component masses space, we choose to perform the KDE in the chirp
mass and mass ratio space, which are less degenerate and is less prone to error
from the KDE.

For progenitor parameters $\bm{\theta'}$, we characterize each guess with five
parameters: the two component masses $M_{\rm 1,ZAMS}$ and $M_{\rm 2,ZAMS}$, the
orbital period $t_{\rm orb}$, the eccentricity $e$, and the metallicity $Z$ at
ZAMS. We use a log-uniform prior in sampling $M_{\rm 1,ZAMS}$, $M_{\rm
2,ZAMS}$, $t_{\rm orb}$, and $Z$, and we use a uniform prior for $e$.
The range follows the range for the optimization range as given by table
\ref{tab:parameters}. Note that the progenitor formation redshift is not
obtained through the root-finding process because the formation redshift does
not intrinsically affect the evolution of the binary. Instead, we compute the
time it takes for the binary to evolve from formation to the merger and add this
time to the lookback time when a GW event is observed and limit the total time
to merger to be less than $13.7\,\rm{Gyr}$. Using the total lookback time, we
can compute the redshift of the binary at ZAMS formation following the Planck
2018 cosmological model \citep{Planck2018}. The main benefit of post-processing
the redshift in this way is that we do not rely on a particular assumption of
star formation rate (SFR) distribution when we solve for the posterior
distribution in redshift. This means we can put the prior on formation redshift
(or in general, metallicity-redshfit distribution) in by reweighting the
posterior distribution according to a particular SFR model, and therefore do not
have to rerun the inference every time we change the SFR model. This is
especially helpful since SFR models are still highly uncertain but strongly
impact the local merger rates of BBHs \citep[e.g. ][]{Broekgaarden2021}.

>>>>

We apply the method described in section \ref{subsec:stats} to the
first GW event GW150914 \citep{GW150914}. We use the \texttt{Overall\_posterior}
posterior samples for GW150914, publicly available from the Gravitational wave
Open Science Center \citep{LIGOScientific:2019lzm}. The parameters involved in
the analysis and the range we allow for the inference are tabulated in Table
\ref{tab:parameters}. The spin of BHs formed in isolated binaries depends
strongly on the angular momentum transport in massive stars which is still
highly uncertain (see however \citet{Fuller2019, Bavera2020}), therefore we only
consider the two component masses in the observable space $\bm{\theta}$ in both
the root-finding stage and the MCMC stage. Instead of the sampling the posterior
in the two component masses space, we choose to perform the KDE in the chirp
mass and mass ratio space, which are less degenerate and is less prone to error
from the KDE.

For progenitor parameters $\bm{\theta'}$, we characterize each guess with five
parameters: the two component masses $M_{\rm 1,ZAMS}$ and $M_{\rm 2,ZAMS}$, the
orbital period $t_{\rm orb}$, the eccentricity $e$, and the metallicity $Z$ at
ZAMS. We use a log-uniform prior in sampling $M_{\rm 1,ZAMS}$, $M_{\rm
2,ZAMS}$, $t_{\rm orb}$, and $Z$, and we use a uniform prior for $e$.
The range follows the range for the optimization range as given by Table
\ref{tab:parameters}. Note that the progenitor formation redshift is not
obtained through the root-finding process because the formation redshift does
not intrinsically affect the evolution of the binary. Instead, we compute the
time it takes for the binary to evolve from formation to the merger and add this
time to the lookback time when a GW event is observed and limit the total time
to merger to be less than $13.7\,\rm{Gyr}$. Using the total lookback time, we
can compute the redshift of the binary at ZAMS formation following the Planck
2018 cosmological model \citep{Planck2018}. The main benefit of post-processing
the redshift in this way is that we do not rely on a particular assumption of
star formation rate (SFR) distribution when we solve for the posterior
distribution in redshift. This means we can put the prior on formation redshift
(or in general, metallicity-redshfit distribution) in by reweighting the
posterior distribution according to a particular SFR model, and therefore do not
have to rerun the inference every time we change the SFR model. This is
especially helpful since SFR models are still highly uncertain but strongly
impact the local merger rates of BBHs \citep[e.g. ][]{Broekgaarden2021}.
